---
title: "Lab 5 (Gracer)"
author: "Allison Gracer"
date: "10/25/2021"
output: 
  html_document: 
    theme: journal
    toc: yes
    code_folding: hide
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals

In this section, we'll use the `t.test()` function to calculate confidence intervals. 

### Example 1

Create a single mock sample containing a number of alues, then learn to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too. 

```{r}
# Create a mock sample (create 1 vector of values) `c()` is how we create a vector

otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths)

# find the standard deviation
otter_sd <- sd(otter_lengths)
```
what does this 95% confidence interval actually mean? 

Answer: the confidence interval means that we would expect if we took multiple samples from this population and calculated a CI for each these, we expect 95% of those CI to contain the true population mean. 

mean otter length is 36.9 inches with a 95% confidence interval of [29.1, 44.7] inches. (original)

What are some really important pieces of information missing if my audience is only going to read the above statement?

Updated: 
Mean otter length is 36.9 inches $\pm$ 9.3 mean($\pm$ sd, n = 8) with a 95% confidence interval of [29.1, 44.7] inches.

  - sample size (n = 8)
  - $\pm$ 9.3 mean($\pm$ sd)
  
We do not want a human gap, we want to use in-line referencing. We need to store the outputs as something


##### How to call elements of a list

objectname$valuename

i.e. otter_ci$p.value

*** type t.test into help for list of operations ***

#### Now, using in-line referencing

Mean otter length is `r otter_ci$estimate`

you can apply things to this in-line code chunk (ex. lets round to 1 decimal place and add units)

Mean otter length is `r round(otter_ci$estimate, 1)` inches. With a 95% confidence interval of [`r otter_ci$conf.int[1]`], [`r round(otter_ci$conf.int[2], 1)`]

this [r otter_ci$conf.int[1]] is saying pull from 

hover over this mini in-line code chunk ans hit command + return to see the value

This process of writing things with in-line code feels tedious at first, but is a huge step to producing reproducible writing in your scientific reports. 

## Part 2: Two-sample t-tests

If we have 2 independent sample, they do not influence each other, do we have evidence to make us think they are from populatons with different means. 

### Example 1

Make two mock samples, and ask the question: do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populations with the same mean?

```{r}
# Make my mock samples

oak_trees <- c(20, 19, 24, 28, 34, 12, 15, 25)


pine_trees <- c(39, 26, 20, 30, 37, 22, 19, 18)

# Run a two-sample t-test (2-sided, 2 sample - are they different enough in either direction to reject null hyp.)
trees_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: mean heights are the same
# another way to say that: Trees are drawn from populations with the same mean height
# p-value = 0.2871... what is this p-value telling us? 
# p-value is telling us: if these samples are drawn from populations with the same mean height (if these samples were drawn from tree populations that have the same mean height), there is a 28.7% chance of taking random samples from those populations and finding that the sample means are at least as different by the ones that we found by random chance. 

# we would not say this is rigorous or compelling evidence to reject the null hypothesis, we are usually using a significance level of 5%, I want less than a 5% chance before I reject the null hypothesis. 

# this p: almost 30/100 times I would get this difference, meaning I do not have enough evidence to reject the null hypothesis that these are drawn from populations with the same mean. 

# the way to report this, report mean values

```

The mean heights of oak and pine trees were (x +- Y) and (X +- Y), respectively, and the difference was not significant (t(`r trees_t$parameter`) =  `r round(trees_t$statistic, 1)`, p = `r trees_t$p.value`). 

"t(df) = t-statistic, which gets me a p value of = p-value" 

(df) = degree of freedom, tells something about sample size, a measure of sample size. the larger you df the larger your sample size. 

